Topic Scores

### 2019-02-28 Topic Scores.Rmd
update names upload files

#
##LDA_models
load("Output/LDA_overview.RDATA")

#
##Topic Models test for ideal number of topics
load("Output/LDA_ntopics_description.RDATA")
load("Output/LDA_ntopics_overview.RDATA")

@@

save(kw, file="App/Recommender System/LDA_keyword_DELETE_.RDATA")
```

>>>>

#
##LDA_models
#load("Output/LDA_overview.RDATA") #replace with underneath
load("Output/topic_model.RDATA")

@@

save(kw, file="App/Recommender System/LDA_keyword_DELETE_.RDATA")
```
### Saving files for APP
```{r keywords}
load("Output/topic_model.RDATA")

save(list_nam, kw,
     file = "App/Recommender System/topic_model.RDATA")

rm(list_nam)
```
